---
title: "Population Weighted Coverage"
output:
  html_document:
    toc: true
output_file: "../03_output/my_report.html"
editor_options: 
  chunk_output_type: console
---


```{r, echo=FALSE, include=FALSE}
knitr::opts_knit$set(output.dir = "../03_output")


library(here, warn.conflicts = FALSE)
library(tidyverse, warn.conflicts = FALSE)
library(haven, warn.conflicts = FALSE)
theme_set(theme_light())

# Final Data with population-weighted coverage
data <- 
  read_dta(here("03_output", "weighted_coverge.dta"))

# View(data)
```

#### 📉 A visualization comparing population-weighted coverage for on-track vs. off-track countries

We observe a significant lag in off-track countries compared to on-track countries in both development outcomes covering **Antenatal care (ANC4)** and **Skilled birth attendance (SBA)**. However, *Antenatal care* coverage (54%) is much worse for off-track countries than *Skilled birth attendance* coverage (67%) for off-track countries. Nevertheless, these estimates should be viewed in the context that our sample of countries is quite limited (50 countries) due to limited convergence of countries in births (000s) and indicators data.

```{r, echo=FALSE, fig.width=6, fig.height=4}

p <- 
data %>% 
  mutate(indicator = ifelse(
    indicator == "anc4", "Antenatal Care (ANC4)", "Skilled Birth Assistance (SBA)"
  )) %>% 
  ggplot(aes(status, val/100, fill=status)) +
  geom_col()+
  facet_wrap(~indicator)+
  labs(x = "", y="",
       fill="Status")+
  scale_y_continuous(labels = scales::percent_format())

print(p)

#Saving Plot in figures folder 
# ggsave(plot = last_plot(),
#        width = 7, height = 6,
#        filename = "04_figures/pop_weighted_coverage.jpeg")

# Saving the output hTML file in the 03_output folder
# rmarkdown::render(here("02_programs","Population_weighted_coverage.Rmd"), output_file = here("03_output","Final_Report.html"))
```


#### Positions applied for:
-   Microdata Harmonization Consultant – Req. #581699
-   Learning and Skills Data Analyst Consultant – Req. #581598
-   Household Survey Data Analyst Consultant – Req. #581656


