---
title: "Population Weighted Coverage"
output:
  html_document:
    toc: true
output_file: "../03_output/my_report.html"
---


```{r, echo=FALSE, include=FALSE}
knitr::opts_knit$set(output.dir = "../03_output")


library(here, warn.conflicts = FALSE)
library(tidyverse, warn.conflicts = FALSE)
library(haven, warn.conflicts = FALSE)
theme_set(theme_light())

# Final Data with population-weighted coverage
data <- 
  read_dta(here("03_output", "weighted_coverge.dta"))

# View(data)
```

#### 📉 A visualization comparing population-weighted coverage for on-track vs. off-track countries

We observe a significant lag in off-track countries compared to on-track countries in both indicators including **Antenatal care (ANC4)** and **Skilled birth attendance (SBA)**. However, *Antenatal care* coverage (54%) is much worse for off-track countries than *Skilled birth attendance* coverage (67%) for off-track countries. Nevertheless, it must be kept in mind that our sample of countries is quite limited due to restrictive coverage in births (000s) data.

```{r, echo=FALSE, fig.width=6, fig.height=4}

p <- 
data %>% 
  mutate(indicator = ifelse(
    indicator == "anc4", "Antenatal Care (ANC4)", "Skilled Birth Assistance (SBA)"
  )) %>% 
  ggplot(aes(status, val_/100, fill=status)) +
  geom_col()+
  facet_wrap(~indicator)+
  labs(x = "", y="",
       fill="Status")+
  scale_y_continuous(labels = scales::percent_format())

print(p)

#Saving Plot in figures folder 
# ggsave(plot = last_plot(),
#        width = 7, height = 6,
#        filename = "04_figures/pop_weighted_coverage.jpeg")

# Saving the output file in the output folder
# rmarkdown::render(here("02_programs","Population_weighted_coverage.Rmd"), output_file = here("03_output","my_report.html"))
```





